---
title: "Clinical results report"
author: "Garzalab"
date: "February 25, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(data.table)
library(moonBook)
library(xtable)
library(afex)
library(effsize)
library(readxl)
library(knitr)

clin1 <- read_rds("outData/cl1.RDS")
clin2 <- read_rds("outData/cl2.RDS")
clin3 <- read_rds("outData/cl3.RDS")
aovClin <- read_rds("outData/aovClin.RDS")
anovaClin <- read_rds("outData/anovaClin.RDS")
chiClin <- read_rds("outData/chiClin.RDS")
chiClin2 <- read_rds("outData/chiClin2.RDS")
chiClin3 <- read_rds("outData/chiClin3.RDS")
tTstClin <- read_rds("outData/tTstClin.RDS")

source('customFunctions.R')

theme_set(theme_linedraw(base_size = 10))
pd <- position_dodge(0.25)
```

## Outcome variables

For the present report, we performed statistical analysis over the results of the following outcome variables: 

+ Craving 
    1. Visual Analogue Scale (VAS)
    2. Cocaine Craving Questionnaire (CCQ)
        + General version
        + Now version
    3. Urine's drug testing (UT)
        + THC
        + Benzodiazepines
        + Cocaine
    4. Pattern of consumption
        + Grams 
        + Frequency
+ Impulsivity
    1. Barratt's Impulsivity Scale 11 (B11)
        + Cognitive subscale
        + Motor subscale
        + Non-planning subscale
        + Total score
+ General improvement
    1. Subjective improvement report
    
## Baseline (T0)

There were no significant differences between any of the results of the outcome variables at baseline between the two stimulation groups.

```{r}
clin1 %>% 
    mutate(Stage = factor(Stage, labels = c("T0", "T1")),
           Group = factor(Group, labels = c("Sham rTMS", "Real rTMS"))) %>% 
    select(1:13) %>% 
    filter(Stage == "T0") %>% 
    select(-Stage) %>% 
    mytable(Group ~ . -Study.ID,
         data = .,
         method = 3) %>% 
    mytable2df()
```

