---
title: "Functional Connectivity Networks' Topology Changes after rTMS in Cocaine Addiction 2.0"
subtitle: "Electric Boogaloo"
author: "Sofia Fernandez"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::pdf_document2:
    toc: true
    fig_caption: true
    keep_md: true
    includes:
        in_header: my_header.tex
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, collapse = TRUE)

library(data.table)
library(readr)
library(here)
library(arsenal)
library(afex)
library(lme4)
library(stargazer)
library(ggplot2)
library(gghalves)
library(ggthemes)
library(ggrepel)
library(extrafont)
library(latex2exp)

X11.options(type = "cairo")
ffont  <- "Merriweather"
```

# Introduction

In this report I present and analyse the data of the ADDIMEX_TMS project.
For the project, participants diagnosed with Cocaine Use Disorder (CUD)
volunteered to take part into a double-blind randomized clinical trial
(Active/Sham) exploring the efficacy of rTMS diminishing the clinical symptoms
of addiction.

Participants were randomly assigned to receive two daily sessions of either
active or sham rTMS over the left-DLPFC for two weeks (10 weekdays).
This consisted in the **closed-label** phase of the study.
After the last day of treatment the group assignment was revealed.
To those of the sham arm we offered to retake 20 more sessions of real rTMS
under the same parameters as the active group.

We acquired both clinical and MRI data at Baseline (T0), two weeks (T1), three
(T2) and six (T3) months. For this **longitudinal phase** only the participants
who started with active stimulation were included in the analysis.

Here I explore the brain functional connectivity of the participants in the
form of global networks constructed from the BOLD signal of their MRI data.
Different metrics of topology are calculated and compared at the different
time-points to see how they are affected by the treatment in the closed-label,
and how they evolve over time in the Longitudinal phase.

```{r, child = here('reports/demog_clin.Rmd')}
```

# Graphs: Raw Thresholding

## Power-264 (with Global Signal)

```{r, child = here('reports/raw_power_gs.Rmd')}
```

## Power-264 (without Global Signal)

```{r, child = here('reports/raw_power_ngs.Rmd')}
```

## Gordon-333 (with Global Signal)

```{r, child = here('reports/raw_gordon_gs.Rmd')}
```

## Gordon-333 (without Global Signal)

```{r, child = here('reports/raw_gordon_ngs.Rmd')}
```

## Schaefer-100 (with Global Signal)

```{r, child = here('reports/raw_schaefer100_gs.Rmd')}
```

## Schaefer-100 (without Global Signal)

```{r, child = here('reports/raw_schaefer100_ngs.Rmd')}
```

## Schaefer-200 (with Global Signal)

```{r, child = here('reports/raw_schaefer200_gs.Rmd')}
```

## Schaefer-200 (without Global Signal)

```{r, child = here('reports/raw_schaefer200_ngs.Rmd')}
```

## Schaefer-400 (with Global Signal)

```{r, child = here('reports/raw_schaefer400_gs.Rmd')}
```

## Schaefer-400 (without Global Signal)

```{r, child = here('reports/raw_schaefer400_ngs.Rmd')}
```

# Graphs: Density Thresholding

## Power-264 (with Global Signal)

```{r, child = here('reports/dens_power_gs.Rmd')}
```

## Power-264 (without Global Signal)

```{r, child = here('reports/dens_power_ngs.Rmd')}
```

## Gordon-333 (with Global Signal)

```{r, child = here('reports/dens_gordon_gs.Rmd')}
```

## Gordon-333 (without Global Signal)

```{r, child = here('reports/dens_gordon_ngs.Rmd')}
```

## Schaefer-100 (with Global Signal)

```{r, child = here('reports/dens_schaefer100_gs.Rmd')}
```

## Schaefer-100 (without Global Signal)

```{r, child = here('reports/dens_schaefer100_ngs.Rmd')}
```

## Schaefer-200 (with Global Signal)

```{r, child = here('reports/dens_schaefer200_gs.Rmd')}
```

## Schaefer-200 (without Global Signal)

```{r, child = here('reports/dens_schaefer200_ngs.Rmd')}
```

## Schaefer-400 (with Global Signal)

```{r, child = here('reports/dens_schaefer400_gs.Rmd')}
```

## Schaefer-400 (without Global Signal)

```{r, child = here('reports/dens_schaefer400_ngs.Rmd')}
```
