---
title: "Functional Connectivity Networks' Topology Changes after rTMS in Cocaine Addiction 2.5"
author: "Sofia Fernandez"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::pdf_document2:
    toc: true
    fig_caption: true
    keep_md: true
editor_options:
  markdown:
    wrap: 72
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, collapse = TRUE)

library(brainGraph)
library(data.table)
library(readr)
library(here)
library(purrr)
library(permute)
library(arsenal)
library(afex)
library(lme4)
library(stargazer)
library(ggplot2)
library(gghalves)
library(ggthemes)
library(ggrepel)
library(extrafont)
library(latex2exp)

X11.options(type = "cairo")
ffont  <- "Merriweather"
```

# Introduction

In this report I present and analyse the data of the ADDIMEX_TMS
project. For the project, participants diagnosed with Cocaine Use
Disorder (CUD) volunteered to take part into a double-blind randomized
clinical trial (Active/Sham) exploring the efficacy of rTMS diminishing
the clinical symptoms of addiction.

Participants were randomly assigned to receive two daily sessions of
either active or sham rTMS over the left-DLPFC for two weeks (10
weekdays). This consisted in the **closed-label** phase of the study.
After the last day of treatment the group assignment was revealed. To
those of the sham arm we offered to retake 20 more sessions of real rTMS
under the same parameters as the active group.

We acquired both clinical and MRI data at Baseline (T0), two weeks (T1),
three (T2) and six (T3) months. For this **longitudinal phase** only the
participants who started with active stimulation were included in the
analysis.

Here I explore the brain functional connectivity of the participants in
the form of global networks constructed from the BOLD signal of their
MRI data. Different metrics of topology are calculated and compared at
the different time-points to see how they are affected by the treatment
in the closed-label, and how they evolve over time in the Longitudinal
phase.

```{r, child = here('reports/demog_clin.Rmd')}
```

