---
title: "Functional Connectivity Networks' Topology Changes after rTMS in Cocaine Addiction 2.5"
output: html_notebook
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, collapse = TRUE)

library(data.table)
library(readr)
library(here)
library(arsenal)
library(afex)
library(lme4)
library(stargazer)
library(ggplot2)
library(gghalves)
library(ggthemes)
library(ggrepel)
library(extrafont)
library(latex2exp)

X11.options(type = "cairo")
ffont  <- "Merriweather"
```

# Demographics and Clinical data

```{r rds-data}
covars <- read_rds(here("data/processed/rds/clin+covars.rds"))
setkey(covars, participant_id, session, group)
att.G <- read_rds(here("data/processed/rds/g_vars_G.rds"))
setkey(att.G, participant_id, session, group)
att.V <- read_rds(here("data/processed/rds/g_vars_V.rds"))
setkey(att.V, participant_id, session, group)
```

```{r derivated-data}
dt.all     <- covars[att.G]
setnames(dt.all, c("threshold", "thresh.method", "global_signal", "atlas"),
         c("t", "t.m", "gs", "a"))

metrics   <- c("density", "strength", "mod.wt", "num.hubs.wt", "E.global.wt",
               "E.local.wt", "E.local", "E.global")
## No SW atts yet
dems      <- c("participant_id", "session", "group")
clins     <- c("bis", "bis_c", "bis_m", "bis_n", "vas", "ccq_n", "ccq_g")
```

## Demographics
After baseline criteria filtering and subsequent exclusion, 50 participants
were randomly assigned to a group and went through baseline data acquisition.

Table \@ref(tab:demog-table) contains a summary of the demographics of these 50 participants initially enrolled.

```{r demog-table, results="asis"}
### Change some levels... Really needed?
# levels(covars$sex)      <- c("Male", "Female")
# levels(covars$tx)[2:3]  <- c("Psych & Pharm", "Pharm")

# Change some labels
labels(covars) <- c(
  age         = "Age (years)",
  educ        = "Education (years)",
  civ         = "Civil status",
  employment  = "Employment (last 3 y)",
  substance   = "Main substance",
  tobacco     = "Smoking",
  cigs_day    = "Cigarettes/day",
  tx          = "Treatment",
  y_start     = "Onset age of cocaine use",
  t_cons      = "Years of cocaine use"
)

# Table
t1 <- tableby(group ~ sex + age + educ + civ + employment + tobacco +
              tobacco_years + cigs_day + substance + tx + y_start + t_cons,
  data = covars[session == "T0"],
  test = FALSE)

summary(t1, title = "(\\#tab:demog-table) Demographic data at baseline", digits = 1)
```

## Dropouts

One of the main drawbacks of the project was the high number of dropouts
throughout the data-acquisition phases. A lot of data would be lost due to
dropouts; six participants didn't complete the two weeks of treatment and only
13 stayed in the program until the six-months time-point.

Most of the analyses are done through mixed-effect models which are robust to
missing data. This allows to maintain the data of those subjects who subsequently
dropped out of the study.

## Covariates

### Clinical data as covariates
The clinical data has already been explored and compared both by the
experimental groups and longitudinally through the different time-points in
another manuscript. For this reason, in this report I focus only in those
variables that showed significant interaction, and their purpose is mainly as covariates for the network analyses.

### In-scanner movement
Head-motion is one of the main sources for artefacts in functional MRI data.
Although some of the noise related to motion can be removed at the
pre-processing steps; residual artefacts can still remain in cases of elevated
motion, especially when dealing with patient populations. Because of this,
frame-wise displacement is treated as a covariate in the models.

## Clinical Data

### Acute phase
In table \@ref(tab:summary-acute) are summarized by experimental group and
session (before and after treatment) the main clinical variables, self-report of consumption (frequency and weight) and in-scanner head movement.

The clinical scores of craving (Viusal Analog Scale) and impulsivity at this
stage are represented in figure \@ref(fig:acute-clin).

```{r summary-acute, results = "asis"}
# Labels
labels(covars)   <- c(
  bis          = "BIS-11",
  bis_c        = "BIS-11 Cognitive",
  bis_m        = "BIS-11 Motor",
  bis_n        = "BIS-11 Non-planning",
  vas          = "Visual Analog Scale",
  ccq_n        = "CCQ-Now",
  ccq_g        = "CCQ-General",
  cons_freq    = "Consumption (freq)",
  cons_grams   = "Consumption (g)",
  fd           = "In-scanner movement (mm)"
)

# Table
t2 <- tableby(session ~ sex + age + cons_freq + cons_grams + relapse + status +
  bis + vas + fd,
  data = covars[session %in% c("T0", "T1")],
  strata = group,
  total = FALSE,
  test = FALSE)

summary(t2, title = "(\\#tab:summary-acute) Clinical summary of acute phase", digits = 1)
```

```{r acute-clin, fig.cap = "Clinical scores by experimental group in the acute phase. A) Craving scores by VAS & B) Impulsivity by BIS-11."}
# colms2: dems [-thresh] + clins
columns   <- c(dems, clins)
## WTF is gdp??? CHANGE TO A BETTER NAME... later
dt.clin   <- covars[session %in% c("T0", "T1"), ..columns]

source(here("scripts/raincloudplots.R"))
colrs <- c("#00429d", "#93003a")

vas2x2 <- dt.clin[, .(y_axis = vas, id = participant_id, s = session, group)]
vas2x2[s == "T0", x_axis := 1 ][ s == "T1", x_axis := 2][
  group == "Real", x_axis := x_axis + 0.01][  ## Change to 2 for double x axis
  , jit := jitter(x_axis, amount = .1)]

p1 <- rc_repmes_2x2(vas2x2, fills = colrs, colors = colrs,
                    groups = c("Sham", "Real")) +
  scale_x_continuous(breaks = c(1,2), labels = c("Pre", "Post"),
                     limits = c(0.4,2.6)) +
  guides(col = FALSE) +
  labs(y = "VAS Total") +
  theme_tufte(base_size = 14) +
  theme(text = element_text(size = 14, family = ffont),
        axis.title.x = element_blank(),
        axis.ticks = element_blank())

bis2x2 <- dt.clin[, .(y_axis = bis, id = participant_id, s = session, group)]
bis2x2[s == "T0", x_axis := 1 ][ s == "T1", x_axis := 2][
  group == "Real", x_axis := x_axis + 0.01][  ## Change to 2 for double x axis
  , jit := jitter(x_axis, amount = .1)]

p2 <- rc_repmes_2x2(bis2x2, fills = colrs, colors = colrs,
                    groups = c("Sham", "Real")) +
  scale_x_continuous(breaks = c(1,2), labels = c("Pre", "Post"),
                     limits = c(0.4,2.6)) +
  guides(col = FALSE) +
  labs(y = "BIS Total") +
  theme_tufte(base_size = 14) +
  theme(text = element_text(size = 14, family = ffont),
        axis.title.x = element_blank(),
        axis.ticks = element_blank())

cowplot::plot_grid(p1, p2, labels = "AUTO", label_size = 18, nrow = 2)
```

### Maintenance phase
To explore the longitudinal changes observed by the rTMS treatment.
The labels for the maintenance phase are the same for both arms.

Main clinical data for all participants with this recording are summarized in
table \@ref(tab:summary-maintenance) and the clinical changes for craving and
impulsivity are represented in figure \@ref(fig:long-clin).

```{r summary-maintenance, results = "asis"}
t3 <- tableby(session ~ sex + age + cons_freq + cons_grams + relapse + status +
  bis + vas + fd,
  data = covars[group == "Real"],
  total = FALSE,
  test = FALSE)

summary(t3, title = "(\\#tab:summary-maintenance) Clinical summary of maintenance phase", digits = 1)
```

```{r long-clin, fig.cap = "Clinical scores across all stages: A) Craving scores by VAS & B) Impulsivity by BIS-11."}
columns <- c(dems[-3], clins)
dt.clin.long <- covars[group == "Real", ..columns]

colrsl <- c("#00429d", "#35739a", "#c8004c", "#93003a")

vasl <- dt.clin.long[, .(y_axis = vas, id = participant_id, s = session)]
vasl[s == "T0", x_axis := 1 ][ s == "T1", x_axis := 2][s == "T2", x_axis :=3][
  s == "T3", x_axis := 4][, jit := jitter(x_axis, amount = .09)]

p3 <- rc_repmes(vasl, times = 4, fills = colrsl, colors = colrsl) +
  scale_x_continuous(breaks = c(1:4), labels = unique(covars[,session]),
                     limits = c(0.9, 5.2)) +
  labs(y = "VAS Total") +
  theme_tufte(base_size = 14) +
  theme(text = element_text(size = 14, family = ffont),
        axis.title.x = element_blank(),
        axis.ticks = element_blank())

bisl <- dt.clin.long[, .(y_axis = bis, id = participant_id, s = session)]
bisl[s == "T0", x_axis := 1 ][ s == "T1", x_axis := 2][s == "T2", x_axis :=3][
  s == "T3", x_axis := 4][, jit := jitter(x_axis, amount = .09)]

p4 <- rc_repmes(bisl, times = 4, fills = colrsl, colors = colrsl) +
  scale_x_continuous(breaks = c(1:4), labels = unique(covars[,session]),
                     limits = c(0.9, 5.2)) +
  labs(y = "BIS Total") +
  theme_tufte(base_size = 14) +
  theme(text = element_text(size = 14, family = ffont),
        axis.title.x = element_blank(),
        axis.ticks = element_blank())

cowplot::plot_grid(p3, p4, labels = "AUTO", label_size = 18, nrow = 2)
```